Using Fundamental Measure Theory to treat the Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-08-14 papers/pair-correlation/paper.tex
minor notational fixes in pair paper Tested everything on bingley.

\section{What is our new idea?}
We approximate the pair correlation with the average of two radial
distribution functions, evaluated at the distance between the two
points, that are themselves functions of our published pair
correlation at contact $g_{sigma}$ evaluated at the two points.

@@

\begin{align}
  g(|\rr|) &= 1 + g_{sigma}e^{-x_0(r-\sigma)} + x_1g_{sigma}sin(x_2(r-\sigma))e^{-x_3(r-\sigma)}\\
  &~~-x_4g_{\sigma}^2sin(x_5(r-\sigma))e^(-x_6(r-\sigma))
\end{align}

@@

%% The homogeneoues limit $g_{sigm}$ can be calculated using the well
%% known and very successful Carnahan Starling equation while the
%% homogeneous limit radial distribution function can be calculated using
%% Monte-Carlo methods.  We used these calculations in a least squares
%% fit along the data points at increasing radial distances in order to
%% fit the perameters of our more general pair correlation function.  Our
%% function will therefore approach the most accurate solution possible
%% in the homogeneous limit.  Created a function that has the form of an
%% expansion in powers of $g_{sigma}$.  $g_{sigm}$ in the homogeneous
%% limit can be calculated using the well known and very successful
%% Carnahan Starling equation.  has a well known and Perameters in the
%% expansion where fit
\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figs/ghs-g}\\
  \includegraphics[width=\columnwidth]{figs/ghs-g-ghs}
  \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
\end{figure}
\section{What does it look like (graphs that show the function itself)?}
\subsection{Separable fit to the radial distribution function}
Figure~\ref{fig:radial-distribution} shows...

>>>>

\section{What is our new idea?}
We approximate the pair correlation with the average of two radial
distribution functions, evaluated at the distance between the two
points, that are themselves functions of our published pair
correlation at contact $g_{\sigma}$ evaluated at the two points.

@@

\begin{align}
  g(|\rr|) &= 1 + g_{\sigma}e^{-x_0(r-\sigma)} + x_1g_{\sigma}\sin(x_2(r-\sigma))e^{-x_3(r-\sigma)}\\
  &~~-x_4g_{\sigma}^2\sin(x_5(r-\sigma))e^(-x_6(r-\sigma))
\end{align}

@@

%% The homogeneoues limit $g_{sigm}$ can be calculated using the well
%% known and very successful Carnahan Starling equation while the
%% homogeneous limit radial distribution function can be calculated using
%% Monte-Carlo methods.  We used these calculations in a least squares
%% fit along the data points at increasing radial distances in order to
%% fit the perameters of our more general pair correlation function.  Our
%% function will therefore approach the most accurate solution possible
%% in the homogeneous limit.  Created a function that has the form of an
%% expansion in powers of $g_{\sigma}$.  $g_{sigm}$ in the homogeneous
%% limit can be calculated using the well known and very successful
%% Carnahan Starling equation.  has a well known and Perameters in the
%% expansion where fit
\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figs/ghs-g}\\
  \includegraphics[width=\columnwidth]{figs/ghs-g-ghs}
  \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
\end{figure}
\section{What does it look like (graphs that show the function itself)?}
\subsection{Separable fit to the radial distribution function}
Figure~\ref{fig:radial-distribution} shows...
